PanGraph: scalable bacterial pan-genome graph construction \\ Supplementary Information

### 2023-03-16 supplementary.tex
Update on Overleaf.

              \item We check that no prior merges have been performed on the same two pancontigs. Sometimes multiple matches are found on the same pancontig, and in this case we prioritize the ones with more negative pseudo-energy. Any following match on the same pancontig will be discarded at this step. It will however be performed later on in the self-map phase of the algorithm (see step 4).

@@

              \item The original starting pancontigs are then removed from the pangenome graph, and no new merges can be performed on them at this step of the algorithm. The newly-created pancontigs are added to the graph and the corresponding paths are updated.

@@

    \item Once the list of all matches has been exhausted the two graphs have been merged into one. However at the previous stage only one merger could be performed per pancontig, which could be insufficient to collapse all of the homology contained in the graph. To this end we repeat the procedure described in step 3, but instead of looking for matches between pancontigs of two different graphs, we perform an all-against-all homology search between all pancontigs in the same graph. Merges are performed following the same rules, and this procedure is repeated until no new merges can be performed.

@@

As graphs are propagated along the guide tree more and more merges are performed. This makes pancontigs progressively shorter but their alignments deeper.\\

>>>>

              \item We check that no prior mergers have been performed on the same two pancontigs. Sometimes multiple matches are found on the same pancontig, and in this case we prioritize the ones with more negative pseudo-energy. Any following match on the same pancontig will be discarded at this step. It will however be performed later on in the self-map phase of the algorithm (see step 4).

@@

              \item The original starting pancontigs are then removed from the pangenome graph, and no new mergers can be performed on them at this step of the algorithm. The newly-created pancontigs are added to the graph and the corresponding paths are updated.

@@

    \item Once the list of all matches has been exhausted the two graphs have been merged into one. However at the previous stage only one merger could be performed per pancontig, which could be insufficient to collapse all of the homology contained in the graph. To this end we repeat the procedure described in step 3, but instead of looking for matches between pancontigs of two different graphs, we perform an all-against-all homology search between all pancontigs in the same graph. Mergers are performed following the same rules, and this procedure is repeated until no new mergers can be performed.

@@

As graphs are propagated along the guide tree more and more mergers are performed. This makes pancontigs progressively shorter but their alignments deeper.\\
